---
title: "Week 11 Lecture Assignment"
author: "Lizzy Sterling"
date: "11/7/2017"
output: rmarkdown::github_document
---

# Unit 11: Modeling Financial Data

#### Description: This assignment is for educational purposes only. We are taking financial data and exploring it in order to figure out general trends and patterns of a time series. We are practicing using log returns to make these assumptions. 
```{r, echo=TRUE, include=FALSE}
library(tseries)
```

### S&P 500 (^GSPC)
####    SNP - SNP Real Time Price. Currency in USD
TODO: Download the data of SP500 '^gspc'.
```{r, echo=TRUE}
SNPdata <- get.hist.quote('^gspc',quote="Close")
```
TODO: Calculate the log returns, which is the subtraction of log(lag(SNPdata)) and log(SNPdata)
```{r, echo=TRUE}
SNPret <- log(lag(SNPdata)) - log(SNPdata)
SNPret <- SNPret[!is.na(SNPret)] #getting rid of the NAs
```
TODO: Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
```{r, echo=TRUE}
SNPvol <- sd(SNPret) * sqrt(250) * 100 
SNPvol
```

Define getVol function for volatility
```{r, echo=TRUE}
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}
```

Calculate volatility over entire length of series for various three different decay factors: 10 30. 100
```{r, echo=TRUE}
volest <- getVol(10, SNPret)
volest2 <- getVol(30, SNPret)
volest3 <- getVol(100, SNPret)
```

Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
```{r, echo=TRUE}
plot(volest,type="l")

# TODO: Add connected line segments for volest2 with the parameters: type="l",col="red"
lines(volest2, type="l", col="red") 
```
